### 2022-06-13 paper.tex
minot

Our nearest-neighbor-count score $\text{nnc}_k$, is based on the $\Gamma$-score \citep{Kireeva_2014} and is calculated as follows. For each cell $j$, we count how many of its $k$ nearest neighbors have been assigned to the same cluster as cell $j$. We denote this count $a^k_j$. We consider a cell as ``well-assigned'' if $a^k_j>\theta k$, where we have chosen $\theta=0.9$. In other words, a cell is ``well-assigned'' if at least 90\% of its $k$ nearest neighbors have been assigned the same class as the cell under consideration.

>>>>

Our nearest-neighbor-count score $\text{nnc}_k$, is based on the $\Gamma$-score \citep{Kireeva_2014} and is calculated as follows. For each cell $j$, we count how many of its $k$ nearest neighbors have been assigned to the same cluster as cell $j$. We denote this count $a^k_j$. We consider a cell as ``well-assigned'' if $a^k_j>\theta k$, where we have chosen $\theta=0.9$. In other words, a cell is ``well-assigned'' if at least 90\% of its $k$ nearest neighbors have been assigned to the same class as the cell under consideration.
